---
title: "Regions of the World"
author: "_Louis du Plessis_"
date: '_`r format(Sys.time(), "Last modified: %d %b %Y")`_'
output: github_document
layout: page
editor_options: 
  chunk_output_type: inline
---

This is a list of admin regions of the world, for easy reference and automatic parsing of epidemiological and genetic data. 

The data were extracted from the [GADM v3.6 database](https://gadm.org/data.html)

The list includes the following divisions:
- admin0: Country level
- admin1: Province/state/region level
- admin2: County/prefecture/district level
- admin3: ...
- admin4: ...
- admin5: ...

Note that higher-level divisions are only present for some countries. 

The outputs are stored in `data/admin_*.csv`. The script also produces `data/world_*.csv` files (not on the Github repository) that are direct csv dumps from the shape files (contain a few extra fields). 


```{r setup, include=FALSE}
  
    library(rgdal)

    knitr::opts_chunk$set(tidy=FALSE, cache=FALSE, 
                          message=FALSE, error=FALSE, warning=FALSE, echo=FALSE)
    
    path <- "data/"
    gadm <- "gadm36_levels_shp"
    
```


## Admin 0

```{r world_0, results='asis'}

    cat("\nExtracting admin0 regions...\n\n")

    world_0 <- rgdal::readOGR(dsn=paste0(path, "/", gadm, "/"), layer="gadm36_0", verbose = FALSE)
    admin_0 <- data.frame(GID_0=world_0$GID_0, NAME_0=world_0$NAME_0)
    
    write.csv(world_0, paste0(path, "world_0.csv"), row.names=FALSE)
    write.csv(admin_0, paste0(path, "admin_0.csv"), row.names=FALSE)
    
    cat(paste0(length(world_0), " admin0 regions successfully extracted.\n\n"))
    
    rm(world_0, admin_0)
    
```

## Admin 1

```{r world_1, results='asis'}

    cat("\nExtracting admin1 regions...\n\n")

    world_1 <- rgdal::readOGR(dsn=paste0(path, "/", gadm, "/"), layer="gadm36_1", verbose = FALSE)
    admin_1 <- data.frame(GID_0  = world_1$GID_0, 
                          GID_1  = world_1$GID_1,
                          NAME_0 = world_1$NAME_0, 
                          NAME_1 = world_1$NAME_1,
                          TYPE_1 = world_1$TYPE_1, 
                          ENGTYPE_1 = world_1$ENGTYPE_1)
    
    write.csv(world_1, paste0(path, "world_1.csv"), row.names=FALSE)
    write.csv(admin_1, paste0(path, "admin_1.csv"), row.names=FALSE)
    
    cat(paste0(length(levels(world_1$NAME_1)), " admin1 regions extracted from ", length(levels(world_1$NAME_0)), " admin0 regions.\n\n"))
    
    rm(world_1, admin_1)
    
```


## Admin 2

```{r world_2, results='asis'}

    cat("\nExtracting admin2 regions...\n\n")

    world_2 <- rgdal::readOGR(dsn=paste0(path, "/", gadm, "/"), layer="gadm36_2", verbose = FALSE)
    admin_2 <- data.frame(GID_0  = world_2$GID_0, 
                          GID_1  = world_2$GID_1,
                          GID_2  = world_2$GID_2,
                          NAME_0 = world_2$NAME_0, 
                          NAME_1 = world_2$NAME_1,
                          NAME_2 = world_2$NAME_2,
                          TYPE_2 = world_2$TYPE_2, 
                          ENGTYPE_2 = world_2$ENGTYPE_2)
    
    write.csv(world_2, paste0(path, "world_2.csv"), row.names=FALSE)
    write.csv(admin_2, paste0(path, "admin_2.csv"), row.names=FALSE)
    
    cat(paste0(length(levels(world_2$NAME_2)), " admin2 regions extracted from ", length(levels(world_2$NAME_1)), " admin1 and ", length(levels(world_2$NAME_0)), " admin0 regions.\n\n"))
    
    rm(world_2, admin_2)
    
```


## Admin 3

```{r world_3, results='asis'}

    cat("\nExtracting admin3 regions...\n\n")

    world_3 <- rgdal::readOGR(dsn=paste0(path, "/", gadm, "/"), layer="gadm36_3", verbose = FALSE)
    admin_3 <- data.frame(GID_0  = world_3$GID_0, 
                          GID_1  = world_3$GID_1,
                          GID_2  = world_3$GID_2,
                          GID_3  = world_3$GID_3,
                          NAME_0 = world_3$NAME_0, 
                          NAME_1 = world_3$NAME_1,
                          NAME_2 = world_3$NAME_2,
                          NAME_3 = world_3$NAME_3,
                          TYPE_3 = world_3$TYPE_3, 
                          ENGTYPE_3 = world_3$ENGTYPE_3)
    
    write.csv(world_3, paste0(path, "world_3.csv"), row.names=FALSE)
    write.csv(admin_3, paste0(path, "admin_3.csv"), row.names=FALSE)
    
    cat(paste0(length(levels(world_3$NAME_3)), " admin3 regions extracted from ", length(levels(world_3$NAME_2)), " admin2, ", length(levels(world_3$NAME_1)), " admin1 and ", length(levels(world_3$NAME_0)), " admin0 regions.\n\n"))

    
    rm(world_3, admin_3)
    
```

## Admin 4

```{r world_4, results='asis'}

    cat("\nExtracting admin4 regions...\n\n")

    world_4 <- rgdal::readOGR(dsn=paste0(path, "/", gadm, "/"), layer="gadm36_4", verbose = FALSE)
    admin_4 <- data.frame(GID_0  = world_4$GID_0, 
                          GID_1  = world_4$GID_1,
                          GID_2  = world_4$GID_2,
                          GID_3  = world_4$GID_3,
                          GID_4  = world_4$GID_4,
                          NAME_0 = world_4$NAME_0, 
                          NAME_1 = world_4$NAME_1,
                          NAME_2 = world_4$NAME_2,
                          NAME_3 = world_4$NAME_3,
                          NAME_4 = world_4$NAME_4,
                          TYPE_4 = world_4$TYPE_4, 
                          ENGTYPE_4 = world_4$ENGTYPE_4)
    
    write.csv(world_4, paste0(path, "world_4.csv"), row.names=FALSE)
    write.csv(admin_4, paste0(path, "admin_4.csv"), row.names=FALSE)
    
    cat(paste0(length(levels(world_4$NAME_4)), " admin4 regions extracted from ", length(levels(world_4$NAME_3)), " admin3,  ", length(levels(world_4$NAME_2)), " admin2, ", length(levels(world_4$NAME_1)), " admin1 and ", length(levels(world_4$NAME_0)), " admin0 regions.\n\n"))

    rm(world_4, admin_4)
    
```

## Admin 5

```{r world_5, results='asis'}

    cat("\nExtracting admin4 regions...\n\n")

    world_5 <- rgdal::readOGR(dsn=paste0(path, "/", gadm, "/"), layer="gadm36_5", verbose = FALSE)
    admin_5 <- data.frame(GID_0  = world_5$GID_0, 
                          GID_1  = world_5$GID_1,
                          GID_2  = world_5$GID_2,
                          GID_3  = world_5$GID_3,
                          GID_4  = world_5$GID_4,
                          GID_4  = world_5$GID_4,
                          NAME_0 = world_5$NAME_0, 
                          NAME_1 = world_5$NAME_1,
                          NAME_2 = world_5$NAME_2,
                          NAME_3 = world_5$NAME_3,
                          NAME_4 = world_5$NAME_4,
                          NAME_5 = world_5$NAME_5,
                          TYPE_5 = world_5$TYPE_5, 
                          ENGTYPE_5 = world_5$ENGTYPE_5)
    
    write.csv(world_5, paste0(path, "world_5.csv"), row.names=FALSE)
    write.csv(admin_5, paste0(path, "admin_5.csv"), row.names=FALSE)
    
    cat(paste0(length(levels(world_5$NAME_5)), " admin5 regions extracted from ", length(levels(world_5$NAME_4)), " admin4, ", length(levels(world_5$NAME_3)), " admin3,  ", length(levels(world_5$NAME_2)), " admin2, ", length(levels(world_5$NAME_1)), " admin1 and ", length(levels(world_5$NAME_0)), " admin0 regions.\n\n"))

    
    rm(world_5, admin_5)
    
```



## Session info

```{r sessionInfo, results='markup'}
    sessionInfo()
```